---
title: "Benchmark Evaluation"
author: "Ben Weinstein"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
#TODO establish best practices relating to data location and how to reference in vignettes.
#https://github.com/weecology/NeonTreeEvaluation/issues/12
```


# Submission Format

The format of the submission is as follows

* A csv file
* 5 columns: Plot Name, xmin, ymin, xmax, ymax

Each row contains information for one predicted bounding box.

The plot column should be named the same as the files in the dataset (e.g. SJER_021)

Submissions should be placed in the /submissions folder

```{r}
library(dplyr)
library(NeonTreeEvaluation)
library(reshape2)

submission<-read.csv(file = "../submissions/Weinstein2019.csv")
head(submission)
```
# Evaluation

For each plot compute the precision and recall based on intersection-over-union of 0.5 between the ground truth bounding boxes and the predicted boxes.

```{r,include=FALSE}
results<-submission %>% group_by(plot_name) %>% do(evaluate_plot(.))
```

```{r}
df<-melt(results)
ggplot(df,aes(x=value)) + geom_histogram() + facet_wrap(~variable)
```

