---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  warning = FALSE,
  message = FALSE
)
```

# NeonTreeEvaluation

[![Travis-CI Build Status](https://travis-ci.org/<USERNAME>/<REPO>.svg?branch=master)](https://travis-ci.org/<USERNAME>/<REPO>)

The goal of NeonTreeEvaluation is to automate testing against the NEON Tree Detection Benchmark

# Submission Format

The format of the submission is as follows

* A csv file
* 5 columns: Plot Name, xmin, ymin, xmax, ymax

Each row contains information for one predicted bounding box.

The plot column should be named the same as the files in the dataset (e.g. SJER_021)

```{r}
library(NeonTreeEvaluation)
library(dplyr)
submission<-read.csv(system.file("extdata", "Weinstein2019.csv",package = "NeonTreeEvaluation"))
head(submission)
```

Evalute just one plot

```{r}
df<-submission %>% filter(plot_name=="SJER_052")
evaluate_plot(df)
```
